NFC and burnout in teachers - A replication and extension study

### 2022-02-17 Manuscript/Manuscript.Rmd

Need for Cognition (NFC) is a stable intrinsic motivation to seek out and especially to enjoy effortful cognitive activities [@Cacioppo1982].
As it bridges the gap between cognition and motivation, NFC is considered to be an investment trait [@Stumm2013], and has come to the fore of psychological research in the last years.
NFC can easily be assessed using the Need for Cognition Scale (NCS), a self-report questionnaire with 18 to 34 items [@Cacioppo1982; @Cacioppo1984].
While many studies have found positive associations of NFC with academic performance [@Cazan2014; @Elias2002; @Grass2017; @Lavrijsen2021; @Zheng2020], recent investigations have also looked at NFC as a personal resource in academic and work contexts.
Individuals high in NFC have more positive emotions at the end of the work day [@Rosen2020], higher work motivation, perceive their roles as less ambiguous [@Nowlin2017], are less likely to drop out of college [@Grass2017; @Klaczynski1996], and have less anxiety regarding their course work [@Karagiannopoulou2020].
These findings suggest that individuals high in NFC might be less prone to experience adverse effects of work stress, which range from physical [@Dragano2017; @Steptoe2013] to psychological [@Madsen2017; @Maslach2016; @Wiesner2005].

>>>>

Need for Cognition (NFC) is a stable intrinsic motivation to seek out and especially to enjoy effortful cognitive activities [@Cacioppo1982].
As it bridges the gap between cognition and motivation, NFC is considered to be an investment trait [@Stumm2013], and has come to the fore of psychological research in the last years.
NFC can easily be assessed using the Need for Cognition Scale (NCS), a self-report questionnaire with 18 to 34 items [@Cacioppo1982; @Cacioppo1984]. <!-- den Satz würde ich entweder weglassen oder noch die deutsche NFC Skala mit referenzieren -->
While many studies have found positive associations of NFC with academic performance [@Cazan2014; @Elias2002; @Grass2017; @Lavrijsen2021; @Zheng2020]<!-- von Stumm & Ackerman, 2013 als Metaanalyse mit aufnehmen, dafür 1-2 Einzelstudien raus -->, recent investigations have also looked at NFC as a personal resource in academic and work contexts.
Individuals high in NFC have more positive emotions at the end of the work day [@Rosen2020], higher work motivation, perceive their roles as less ambiguous [@Nowlin2017], are less likely to drop out of college [@Grass2017; @Klaczynski1996], and have less anxiety regarding their course work [@Karagiannopoulou2020].
These findings suggest that individuals high in NFC might be less prone to experience adverse effects of work stress, which range from physical [@Dragano2017; @Steptoe2013] to psychological [@Madsen2017; @Maslach2016; @Wiesner2005] consequences.
